Quantum Hoare Type Theory

### 2020-10-26 ms-paper/ms-paper.tex
Get rid of state function
Revise share example

\lstset{
	basicstyle=\small\ttfamily,
	flexiblecolumns=false,
	basewidth={0.5em,0.45em},
	commentstyle=\color{dkgreen},
	keywordstyle=\bfseries\color{blue},
	stringstyle=\color{violet},
	literate={+}{{$+$}}1 {/}{{$/$}}1 {*}{{$*$}}1 {=}{{$=$}}1
	{>}{{$>$}}1 {<}{{$<$}}1 {\\}{{$\lambda$}}1
	{\\\\}{{\char`\\\char`\\}}1
	{->}{{$\rightarrow$}}2 {>=}{{$\geq$}}2 {<-}{{$\leftarrow$}}2
	{<=}{{$\Leftarrow$}}2 {=>}{{$\Rightarrow$}}2
	{\ .}{{$\circ$}}2 {\ .\ }{{$\circ$}}2
	{>>}{{>>}}2 {>>=}{{>>=}}2
	{|}{{$\vert$}}1 {\\>}{{$\rangle$}}1
	{/\\}{{$\wedge$}}1 {\\/}{{$\vee$}}1
	{\\in}{{$\in$}}1 {\\o}{{$\circ$}}1 {\\Pi}{{$\Pi$}}1
	{\\Phi+}{{$\Phi^+$}}2
	{|->}{{$\mapsto$}}2 {-o}{{$\multimap$}}2
	{o*}{{$\otimes$}}1
	{\\top}{{$\top$}}1
	{\\bot}{{$\bot$}}1
}

@@

\begin{mathpar}
	\inferrule
	{\Delta \vdash N \chk \type{Bit}
		\\ \Delta, x : \type{Qbit}; P \circ (x \mapsto \kw{state}(N)) \vdash E \syn y:B . Q}
	{\Delta; P \vdash x \Leftarrow \kw{init} N; E \syn y:B. (\exists x:\type{Qbit}.Q)}
\end{mathpar}
where x is fresh and \texttt{state} is a function that translates a classical representation of quantum state (such as boolean here) to the equivalent quantum state vector. \todo{TODO}

@@

\subsubsection{Hello Quantum World}
\leavevmode

@@

Verification steps follow:

@@

\subsection{Creating entanglement}
\begin{lstlisting}[language=QHaskell]
share : \Pi a : Qbit.
        {a \in {|+\>, |-\>}}   -- a \in {b, c} is short for Id(a,b) \/ Id(a,c)
           b : Qbit
        {Id(a, b) /\ a \in {|0\>, |1\>}}
      = \a.do b <= init 0;
              apply CNOT to [a, b];
              return b
\end{lstlisting}

>>>>

\lstset{
	basicstyle=\small\ttfamily,
	flexiblecolumns=false,
	basewidth={0.5em,0.45em},
	commentstyle=\color{dkgreen},
	keywordstyle=\bfseries\color{blue},
	stringstyle=\color{violet},
	literate={+}{{$+$}}1 {/}{{$/$}}1 {*}{{$*$}}1 {=}{{$=$}}1
	{>}{{$>$}}1 {<}{{$<$}}1 {\\}{{$\lambda$}}1
	{\\\\}{{\char`\\\char`\\}}1
	{->}{{$\rightarrow$}}2 {>=}{{$\geq$}}2 {<-}{{$\leftarrow$}}2
	{<=}{{$\Leftarrow$}}2 {=>}{{$\Rightarrow$}}2
	{\ .}{{$\circ$}}2 {\ .\ }{{$\circ$}}2
	{>>}{{>>}}2 {>>=}{{>>=}}2
	{|}{{$\vert$}}1 {\\>}{{$\rangle$}}1
	{/\\}{{$\wedge$}}1 {\\/}{{$\vee$}}1
	{\\in}{{$\in$}}1 {\\o}{{$\circ$}}1 {\\Pi}{{$\Pi$}}1
	{\\Phi+}{{$\Phi^+$}}2
	{|->}{{$\mapsto$}}2 {-o}{{$\multimap$}}2
	{o*}{{$\otimes$}}1
	{\\top}{{$\top$}}1
	{\\bot}{{$\bot$}}1
	{=q}{{$=_q$}}2
	{alpha}{{$\alpha$}}1 {beta}{{$\beta$}}1
}

@@

\begin{mathpar}
	\inferrule
	{\Delta \vdash N \chk \type{Bit}
		\\ \Delta, x : \type{Qbit}; P \circ (x \mapsto \ket{N}) \vdash E \syn y:B . Q}
	{\Delta; P \vdash x \Leftarrow \kw{init} N; E \syn y:B. (\exists x:\type{Qbit}.Q)}
\end{mathpar}
where x is fresh.

@@

\subsubsection{Hello Quantum World}
 \todo{TODO}
\leavevmode

@@

Verification steps follow:  \todo{TODO}

@@

\subsection{Creating entanglement}
\begin{lstlisting}[language=QHaskell]
share : \Pi a : Qbit.
        {a =q (alpha |0\> + beta |1\>)}
           (a, b) : (Qbit o* Qbit)
        {(a, b) =q (alpha |00\> + beta |11\>)}
      = \a.do b <= init 0;
              (a, b) <= apply CNot to [a, b];
              return (a, b)
\end{lstlisting}
